Output Summary

### 2020-09-24 03-post-process/output-plots.Rmd
Add plots displaying fit to pre-spawn data

The code used to render this output relies heavily on Staton's 'postpack' package (currently under CRAN review). Take a look at [this vignette](https://bstaton1.github.io/postpack/articles/feature-overview.html) for a primer on how to use it.

@@

@@

All red component are posterior summaries (medians and 95% credible intervals). The black curve is from an `nls()` fit on reconstructed parr and spawners -- the grey region is the confidence interval around this fit (from a parametric bootstrap).

>>>>

The code used to render this output relies heavily on Staton's 'postpack' package (now available on CRAN). Take a look at [this vignette](https://bstaton1.github.io/postpack/articles/feature-overview.html) for a primer on how to use it.

@@

## Spawn Status Data

```{r spawn-status-fits, fig.width = 3.5, fig.height = 5}
par(oma = c(1.5,1.5,0,0))
layout(matrix(c(1,2), 2, 1), heights = c(1, 0.65))
plot_tseries(post_summ(post, "^phi_Sb_Sa["), with(jags_data, carcs_spawned/carcs_sampled)[observable], main = "Successful Spawning")
mtext(side = 2, "Survival Probability", line = 1.5)

at_x = seq(1, length(observable), 4)
par(mar = c(2,2,0,1), yaxs = "i")
mp = barplot(jags_data$carcs_sampled[observable], xaxt = "n", ylim = c(0, max(jags_data$carcs_sampled, na.rm = T)) + c(0, 5))
axis(side = 1, at = mp[at_x], labels = substr( names(jags_data$carcs_sampled[observable]), 3, 4)[at_x])
box()
mtext(side = 2, "Carcasses Sampled", line = 1.5)
mtext(side = 1, "Brood Year", line = 1.5)
```

@@

All red components are posterior summaries (medians and 95% credible intervals). The black curve is from an `nls()` fit on reconstructed parr and spawners -- the grey region is the confidence interval around this fit (from a parametric bootstrap).
